---
title: "R Luminescence version > 0.8.0 </br> - Solid Mouse -"
author: "R Luminescence Team"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Dear **R** Luminescence users!

With the beginning of the new year 2018, we are lifting our **R** package up to version 0.8.0 [CRAN](https://CRAN.R-project.org/package=Luminescence). We are thankful for all the helpful suggestions and comments we received over time. Although this major update comes with some new functions, we focused our efforts on stability and reliability of the code. Below we want to highlight some of the new features. For a full list of changes and particularly the bug fixes, please check the news on the CRAN webpage [here](https://cran.r-project.org/web/packages/Luminescence/news.html). 

```{r, echo = FALSE, message=FALSE}
library(Luminescence)
```

## What's new?

### New analysis functions

#### Tackle environmental dose rates 

Reliably estimating the environmental dose rate is an essential step in every luminescence dating process. The environmental gamma-dose can be either derived from the U, Th and K potassium concentration of the sediment subsamples in the laboratory or
by in-situ measurements in the field. Laboratory measurements tend to become unreliable in case the 
infinite matrix dose assumption does not hold, e.g., due to sedimentary inhomogeneities. In-situ 
measurements with passive dosimeters, such as $\alpha\mbox{-}Al_{2}O_{3}:C$, offer an alternative. 
To ease the data processing needed for such analyses we developed three new **R** functions: 

* `analyse_Al2O3C_ITC()`
* `analyse_Al2O3C_CrossTalk()`
* `analyse_Al2O3C_Measurement()`

Details on the usage of the function and a working example are shipped as package vignette with this 
release.

#### I wanna Rock!

During the last couple of years, there has been a rising trend in rock surface-exposure dating applications. Even though
the potential luminescence dating of rock surfaces was already recognised a couple of decades ago, the recent surge
in dating applications was likely triggered by the important works of Sohbati et al. (2011, 2012a, 2012b). To accommodate for the
new demand to analyse data from rock surface-exposure measurements we included the new function `fit_SurfaceExposure`, which allows fitting the models after Sohbati et al. (2012a, b) to the data.

```{r, eval=FALSE}
## Load example data
data("ExampleData.SurfaceExposure")

## Example 1 - Single sample
results <- fit_SurfaceExposure(ExampleData.SurfaceExposure$sample_1, 
                               mu = 0.9, sigmaphi = 5e-10)
```

```{r, echo = FALSE, fig.align='center', fig.width=4}
data("ExampleData.SurfaceExposure")
results <- fit_SurfaceExposure(ExampleData.SurfaceExposure$sample_1, 
                               mu = 0.9, sigmaphi = 5e-10, cex = 0.9, legend = FALSE, error_bars = FALSE)
```

As seen in the example we also included a new (synthetic) example dataset (`ExampleData.SurfaceExposure`), which you can use 
to play around with the function without the need for own data. 
Note, however, that we regard this function to be still in its **BETA** phase. There has not been much feedback yet, and the integration of the dose rate after Sohbati et al. (2012b) was simplified (fixed dose rate term instead of it being a 
function of depth). For more information on the function and the data be sure to check out the documentation for `?fit_SurfaceExposure` and `?ExampleData.SurfaceExposure`.

#### Another age model?

The minimum age model by Woda and Fuchs (2008) is one of the very few proposed dose models which had not yet been included in the package. 
The idea behind this model is based on the approach by Lepper & McKeever (2002) and determines the dose, which is representative of the age of the deposit, by 
using a Gaussian equation to fit the data. The approach by Woda and Fuchs (2008) refines this model by 
fixing the centre of the Gaussian equation to reach a more robust fitting. 
How does it work? See below for a running example:

```{r, fig.align='center', fig.width=5}
## read example data set
data(ExampleData.DeValues, envir = environment())

## run calculation
results <- calc_WodaFuchs2008(
  data = ExampleData.DeValues$CA1,
   xlab = expression(paste(D[e], " [Gy]"))
 )
```

#### Helper functions 

Sometimes it is the small things that make the difference and ease your life. In this release, 
we included two new helper functions you certainly don't need every day, but which you may eventually use and value. 

1. `convert_Activity2Concentration()`

Gamma-spectrometry measurement results are sometimes provided in 'Bq/kg' instead of the 'ppm', which is 
usual reported in the context of luminescence dating. This function helps to quickly transform 
the numbers: 

```{r}
##construct data.frame
data <- data.frame(
 NUCLIDES = c("U-238", "Th-232", "K-40"),
 VALUE = c(40,80,100),
 VALUE_ERROR = c(4,8,10),
 stringsAsFactors = FALSE)

##perform analysis
convert_Activity2Concentration(data)
```

2. `convert_RLum2Risoe.BINfileData()`

To date, the package supports a large variety of measurement formats and internally converts them to a common data format. 
This approach allows you to mix and merge data from different sources. Someday in the future, however, there is this one colleague who is not using **R** and who will ask you for the measurement data in the BIN/BINX-file 
format. Once data were imported into **R**, however, there was no way back; until today! 
The new function `convert_RLum2Risoe.BINfileData()` allows you to export your `RLum.Analysis` 
objects to BIN/BINX-files and to share them with your colleagues. How? It could not be easier: 

```{r, eval = FALSE}
data(ExampleData.RLum.Analysis, envir = environment())
convert_RLum2Risoe.BINfileData(IRSAR.RF.Data, file = "your/path/output.BIN")
```


# References {-}

Lepper, K., McKeever, S.W.S., 2002. An Objective Methodology For Dose Distribution Analysis. Radiation Protection Dosimetry 101, 349-252. [doi: 10.1093/oxfordjournals.rpd.a005999](https://doi.org/10.1093/oxfordjournals.rpd.a005999)

Sohbati, R., Murray, A., Jain, M., Buylaert, J.P. and Thomsen, K., 2011. Investigating the resetting of OSL signals in rock surfaces. Geochronometria 38(3), 249-258. [doi: 10.2478/s13386-011-0029-2](https://doi.org/10.2478/s13386-011-0029-2)

Sohbati, R., Murray, A.S., Chapot, M.S., Jain, M., Pederson, J., 2012a. Optically stimulated luminescence (OSL) as a chronometer for surface exposure dating. Journal of Geophysical Research 117, B09202. 
[doi: 10.1029/2012JB009383](https://doi.org/10.1029/2012JB009383)

Sohbati, R., Jain, M., Murray, A.S., 2012b. Surface exposure dating of non-terrestial bodies using optically stimulated luminescence: A new method. Icarus 221, 160-166. [doi: 10.1016/j.icarus.2012.07.017](https://doi.org/10.1016/j.icarus.2012.07.017)

Woda, C., Fuchs, M., 2008. On the applicability of the leading edge method to obtain equivalent doses in OSL dating and dosimetry.
Radiation Measurements 43, 26-37.[doi: 10.1016/j.radmeas.2007.12.006](http://dx.doi.org/10.1016/j.radmeas.2007.12.006)
