---
title: "R Luminescence version > 0.8.0 </br> - Solid Mouse -"
author: "R Luminescence Team"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Dear **R** Luminescence users!

Now we have 2018 and we lifting our **R** package up to version 0.8.0 [CRAN](https://CRAN.R-project.org/package=Luminescence). As usual, we are thankful for all the helpful suggestions and comments we received over time. Although this major update comes with some new functions, were focussed on our efforts on stability and reliability. Below we rendered some highlights for you. For a full list of all changes, in particular 
the bug fixes, please check the CRAN webpage [here](https://cran.r-project.org/web/packages/Luminescence/news.html). 

```{r, echo = FALSE, message=FALSE}
library(Luminescence)
```

## What's new?

### New analysis functions

#### Tackle environmental dose rates 

* analyse_Al2O3C_ITC()
* analyse_Al2O3C_CrossTalk()
* analyse_Al2O3C_Measurement()


#### Sureface exposure dating 

* `fit SurfaceExposure()` @tzerk

#### Another age model?

* `calc_WodaFuchs2008()` @coffeemuggler 

#### Helper functions 

We included two helper functions in this release:

* `convert_Activity2Concentration()`

Gamma-spectrometry measurement results are often provided in Bg/kg instead of the `ppm`, which is 
usual reported in the context of luminescence dating. This function helps to quickly transform 
the numbers: 

```{r}
##construct data.frame
data <- data.frame(
 NUCLIDES = c("U-238", "Th-232", "K-40"),
 VALUE = c(40,80,100),
 VALUE_ERROR = c(4,8,10),
 stringsAsFactors = FALSE)

##perform analysis
convert_Activity2Concentration(data)
```

* `convert_RLum2Risoe.BINfileData()`

To date the package supports the import of various measurement formats and treat them similar internally. 


