---
title: "R Luminescence version > 0.8.0 </br> - Solid Mouse -"
author: "R Luminescence Team"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Dear **R** Luminescence users!

Now we have 2018, and we are lifting our **R** package up to version 0.8.0 [CRAN](https://CRAN.R-project.org/package=Luminescence). We are thankful for all the helpful suggestions and comments we received over time. Although this major update comes with some new functions, we had focussed our efforts on stability and reliability. Below we render some highlights for you. For a full list of all changes, in particular, the bug fixes, please check the news on the CRAN webpage [here](https://cran.r-project.org/web/packages/Luminescence/news.html). 

```{r, echo = FALSE, message=FALSE}
library(Luminescence)
```

## What's new?

### New analysis functions

#### Tackle environmental dose rates 

Reliably estimating the environmental dose rate is an essential step in every luminescence dating process. The environmental gamma-dose can be either derived from the U, Th and K potassium concentration of the sediment subsamples in the laboratory or
in situ measurements in the field. Laboratory measurements tend to become unreliable in cases the 
infinite matrix dose assumption does not hold, e.g., due to sedimentary inhomogeneities. In situ 
measurements with passive dosimeters, such as  alpha-Al$_{2}O_{3}:C, offer an alternative. 
To ease the data processing needed for such analyses we developed three new **R** functions: 

* `analyse_Al2O3C_ITC()`
* `analyse_Al2O3C_CrossTalk()`
* `analyse_Al2O3C_Measurement()`

Details on the usage and a working example are shipped as package vignette with this release. 

#### Sureface exposure dating 

* `fit SurfaceExposure()` @tzerk

#### Another age model?

* `calc_WodaFuchs2008()` @coffeemuggler 

#### Helper functions 

We included two helper functions in this release:

* `convert_Activity2Concentration()`

Gamma-spectrometry measurement results are often provided in Bg/kg instead of the `ppm`, which is 
usual reported in the context of luminescence dating. This function helps to quickly transform 
the numbers: 

```{r}
##construct data.frame
data <- data.frame(
 NUCLIDES = c("U-238", "Th-232", "K-40"),
 VALUE = c(40,80,100),
 VALUE_ERROR = c(4,8,10),
 stringsAsFactors = FALSE)

##perform analysis
convert_Activity2Concentration(data)
```

* `convert_RLum2Risoe.BINfileData()`

To date the package supports the import of various measurement formats and treat them similar internally. 


