---
title: "RLumModel - Models and parameters"
author: "Sebastian Kreutzer (Earth Sciences and Geography, Abersytwyth University, UK) & Johannes Friedrich (University of Bayreuth, DE)"
date: '`r Sys.Date()`'
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
    fig_height: 5
    fig_width: 5
    number_sections: yes
    toc: yes
bibliography: RLumModel.bib
vignette: |
  %\VignetteIndexEntry{RLumModel - Models and parameters} 
  %\VignetteEncoding{UTF-8}{inputenc}
  %\VignetteEngine{knitr::rmarkdown} 
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'h', fig.align = 'center')
```

```{r, echo=FALSE, message = FALSE}
library(RLumModel)
library(gt)
```

# Models and parameters

The table lists the parameters used in the different models implemented 
in `'RLumModel'`. The tables are automatically extracted from the output of the
function `.set_pars()` to provide a better human-readable output format. 

It is common in the published literature to assign descriptive names to the energy levels. 
Obviously, this labelling is open to interpretation and has nothing carved in stone. Moreover, it depends partly on the model
and the authors' understanding. 

Although different models are implemented in `'RLumModel'`, we did not 
assess whether they are meaningful but implemented them to 
allow direct comparison. Please remember that the main differences between models narrow down to the assumed concentration of 
specific levels (for instance, $N$). Sometimes models have different 
concentration levels underpinned by experiments that were or were not suitable to validate those changes. However, sometimes concentration levels differ because the authors modified them by try and error. 
Either way, we **strongly recommend** double-checking the underlying assumption of each model in the original article.
 

LEVEL     |LABEL              |DESCRIPTION
----------|-------------------|----------------
trap_1    | 110ºC TL          | Electron trap associated with the 110ºC TL peak
trap_2    | 230ºC TL          | Electron trap associated with the 230ºC TL peak
trap_3    | OSL_fast          | Electron trap feeding the OSL fast component
trap_4    | OSL_medium        | Electron trap linked to the OSL medium component
(trap_5)  | OSL_deep/OSL_slow1| Electron trap linked to the first OSL slow component or the deep OSL trap
(trap_6)  | OSL_slow2/TT-OSL  | Electron trap linked to the second OSL slow component or the TT-OSL trap
(trap_7)  | OSL_slow3/BT-OSL  | Electron trap linked to the third OSL slow component or the BT-OSL trap
(trap_8)  | OSL_deep          | Electron trap linked to the deep OSL trap
centre_1  |R1 centre          | Reservoir centre 1, non-radiative, thermally unstable
centre_2  |R2 centre          | Reservoir centre 2, non-radiative, thermally unstable
centre_3  |K centre           | Killer centre, non-radiative recombination centre
centre_4  |L centre           | Luminescence centre 

The levels given in parentheses change according to the maximum number of levels in the model. 
For instance, if the model has only five electron traps, level `trap_5` is associated with 
the deep OSL electron trap. However, if the model has traps associated with slow components, 
as in @Bailey_2001, the OSL deep trap is associated with the `trap_8` [cf. @Friedrich_2016].

*Please note that, unlike in the table above, the parameter tables below are generated
automatically from the models implemented in `'RLumModel'`. Therefore the labelling
is kept very general.*

```{r, echo=FALSE, results='asis'}
## get models
models <- .set_pars()[grepl(pattern = "^(?!custom)",.set_pars(), perl = TRUE)]

l <- lapply(models, function(x){
  temp <- .set_pars(x)
  n <- temp$n@data$n
  temp$n <- NULL
  c(temp, list(n = n))
  
})

## get the maximum number of number of electron traps 
n_levels <- max(vapply(l, function(x) length(x$B), numeric(1)))
n_trap_max <- max(vapply(l, function(x) sum(x$B == 0), numeric(1)))

##generate matrices
m <- matrix(NA, nrow = n_levels + 2, ncol = length(models))
colnames(m) <- models
rownames(m) <- c(
  paste0("trap_", 1:n_trap_max), 
  paste0("centre_", ((n_trap_max + 1):(nrow(m) - 2) - (n_trap_max))),
  "n_c",
  "n_v")

## fill matrices
for (p in names(l[[1]])[!names(l[[1]]) %in% c("units", "names","model")]) {
  for (i in 1:length(l)) {
    ##traps
    m[which(l[[i]]$B == 0),i] <- l[[i]][[p]][which(l[[i]]$B == 0)] 
    ##hole
    if (!is.null(l[[i]][[p]])) 
      m[(n_trap_max + 1):(n_trap_max + length(which(l[[i]]$B != 0))),i] <- l[[i]][[p]][which(l[[i]]$B != 0)] 
  
    ##n
    if (p == "n")
      m[(nrow(m) - 1):nrow(m),] <- l[[i]][[p]][(length(l[[i]][[p]])-1):length(l[[i]][[p]])]
  }
  
  ## create data.frame
  df <- as.data.frame(m)
  
  ## remove all NA rows
  df <- df[rowSums(is.na(m)) != length(models),]
  
  ## add running number
  df <- cbind(`#` = 1:nrow(df), df)
  
  ## create table object
  g <- gt::gt(df,rownames_to_stub = TRUE, ) %>%
    gt::tab_header(
      title = paste0(p, " (", l[[i]]$units[p],")"), 
      subtitle = l[[i]]$names[p]) %>%
    gt::opt_align_table_header(align = c("left")) %>%
    gt::tab_style(style = list(
      cell_fill(color = "lightyellow"),
      cell_text(weight = "bold")
      ),
    locations = cells_body(
      columns = `#`)) %>%
    gt::tab_style(style = list(
      cell_text(weight = "bold")
      ),
    locations = gt::cells_column_labels())
  
  pander::pandoc.header(paste0("Parameter: ", p), level = 2)
  print(g)
  
}

```

# References {-}
